---
title: "Gov 50 Final Project"
author: "Nishant Mishra"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



\newcommand{\noin}{\noindent}    
\newcommand{\Var}{\text{Var}}    
\newcommand{\Cov}{\text{Cov}}    


```{r}
set.seed(139)
data <- read.csv('data/MERGED2018_19_PP.csv')
```

```{r}
new_data <- data[data$DISTANCEONLY == 0, ]
# new_data <- new_data[new_data$CURROPER == 1, ]
```

```{r}
columns <- c('HIGHDEG', 'REGION', 'UGDS_WHITE', 'UGDS_BLACK', 'UGDS_HISP', 'UGDS_ASIAN', 'UGDS_AIAN', 'UGDS_NHPI', 'ADM_RATE', 'C150_4', 'C150_L4', 'SAT_AVG', 'UGDS', 'FSEND_COUNT', 'MEDIAN_HH_INC', 'POVERTY_RATE', 'UGDS_MEN', 'NPT4_PUB', 'NPT4_PRIV', 'UG25ABV', 'UG_NRA', 'PCIP04', 'PCIP05', 'PCIP09', 'PCIP11', 'PCIP14', 'PCIP23', 'PCIP26', 'PCIP27', 'PCIP38', 'PCIP42', 'PCIP45', 'PCIP50', 'PCIP51', 'PCIP52', 'PCIP54')
new_data <- new_data[columns]
```

```{r}
UGDS_MEN  = as.numeric(new_data$UGDS_MEN)[!is.na(new_data$UGDS_MEN )]
hist(UGDS_MEN)
NPT4_PUB = as.numeric(new_data$NPT4_PUB )[!is.na(new_data$NPT4_PUB  )]
hist(NPT4_PUB)
summary(NPT4_PUB)
NPT4_PRIV = as.numeric(new_data$NPT4_PRIV )[!is.na(new_data$NPT4_PRIV )]
hist(NPT4_PRIV)
summary(NPT4_PRIV)
boxplot(NPT4_PUB, NPT4_PRIV,
        horizontal=TRUE,
        names=c("NPT4_PUB (public)","NPT4_PRIV (private)"),
        col=c("thistle","wheat"),
        xlab="Price",
        main="Average net price for undergraduate institutions")
